---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sdtmsyn

<!-- badges: start -->
<!-- badges: end -->

sdtmsyn is an R package to generate synthetic SDTM data for fictional clinical
PK studies with the drug 'examplinib'.

The generated data are based on simple heuristics for vital signs and a popPK
model for the drug and its metabolite and reflect a realistic participant
population.

## Installation

You can install the development version of sdtmsyn like so:

``` r
devtools::install_github("rstrotmann/sdtmsyn)
```

## Example

This is a basic example to generate SDTM domains DM, VS, EX and PC for a
fictional food effect study with 'examplinib':

```{r example, warning = F}
library(sdtmsyn)

sdtm <- make_study_fe()
names(sdtm)
head(sdtm$dm, 5)
head(sdtm$vs, 5)
head(sdtm$ex, 5)
head(sdtm$pc, 5)
```

